\documentclass[12pt,a4paper]{article}
\usepackage[top=25truemm,bottom=25truemm,left=25truemm,right=25truemm]{geometry}


\begin{document}
This manuscript provides an overview of the materials and technologies for manipulating and charactering surface polaritons (SPs) within MIR and FIR for those not familiar in this research field, with a special emphasis on experimental methodology. The background, fundamental properties of infrared SPs, materials and apparatus available, and common experimental configurations are clearly summarized, and the authors have been referring to the main contribution to this field throughout their paper. The paper is logically organized, clearly written and can be published with minor corrections. 

\noindent
Some minor considerations:
\begin{itemize}
%\item Misleading statement in the first paragraph in Section 1: "SPPs are predominantly observed in the shorter wavelength visible and near-infrared (NIR) spectral ranges". 

%sec2
\item There is a missing period (.) at the end of equation 2. 

\item The fundamental condition for the grading coupling $k_{SP} = k_0 sin \theta + \frac{2m \pi}{d}$ or the corresponding formula is missing in the manuscript. While the authors depicts the condition by using an analogy, the additional mathematical representation must help the readers' understanding. 

\item The hidden x-axis label of operation frequency within the Fig. 2b needs to be shown.

\item The equation $S(\lambda,T_i) = R(\lambda)(s(\lambda)+r(\lambda,T_i))$ at the second paragraph of the subsection entitled "Thermal Emission and Emissivity Measurements" in Section 2, should be replaced by $S(\lambda,T_i) = R(\lambda)(s(\lambda,T_i)+r(\lambda))$. Similarly, $B(f,T_i)$ and $b(f,T_i)$ should be replaced $B(\lambda,T_i)$ and $b(\lambda,T_i)$ respectively at the same paragraph. 

%sec3
\item The extensive experimental techniques are lengthy described in the section 3 for the important part of this tutorial.  For readers' convenience an outlook of the scopes and advantages must be explained at the educational viewpoint. 

\item Since "Mylar" is the trade name of the commercial product and the prospective readers might be less familiar with it, its chemical name and property should be addressed.

%sec4
\item A possible misspelling of SPhPs at the section 4.1: 
"{\it SPhPs} in SiC have been exploited for surface sensing, with detection possible down to a few atomic layers, while hBN resonantors have been demonstrated for femtomolar sensitivity using the surface enhanced IR absorption (SEIRA) effect."

\item  In the reference section, the abbreviation style of the journals contains multiple inconsistencies: Both "Applied Physics Letter" and "Appl. Phys. Lett." are used at the same time. Similarly both "Physical Review Letter" and "Phys. Rev. Lett." is used. 

\end{itemize}

\end{document}